%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Nadide}{Pasali}{ \urlstyle{same}\url{http://nadide.github.io/} \\
\href{mailto:nadidepasali@gmail.com}{nadidepasali@gmail.com} | 832.951.2848
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{North American}
\subsection{University (NAU)}

\descript{BS in Computer Science}
\location{May 2019 | Houston, Tx}
Conc. in Software Engineering \\
Conc. in Computer Network \\

\location{ Major GPA: 3.81 / 4.0}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Website:// \href{http://nadide.github.io/}{\custombold{nadide,github.io}} \\
Github:// \href{https://github.com/nadide}{\custombold{nadide}} \\
LinkedIn://  \href{https://www.linkedin.com/in/nadidepasali/}{\custombold{nadidepasali}} \\
Twitter://  \href{https://twitter.com/nadidepasali}{\custombold{@nadidepasali}} \\
HackerRank://  \href{https://www.hackerrank.com/nddpasali}{\custombold{nddpasali}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Courses}
\subsection{Computer Science}
CS I (C Language) \\
CS II (Java Language) \\
Data Structures \\
System Programming \\
Database Systems \\
Programming Languages \\
Web Application Development \\
Computer Networks \\
Computer Organization \\
\sectionsep

\subsection{Mathematics}
Statistics \\
Discrete Math \\
Calculus I \\
Calculus II \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Expert:}
C/C++ \textbullet{} Python \textbullet{} Algorithms \\
LINUX \textbullet{} Git/GitHub \\
\location{Advance:}
Java \textbullet{} HTML/CSS \textbullet{} JavaScript \\
MySQL \textbullet{} Matlab/Octave \textbullet{} \LaTeX \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\iftrue
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{ACM-W}
\descript{| Chapter Chair }
\location{Aug 2016 – Present | Houston, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Lead a group of 15-20 female computer science students.
\item Organized activities and projects that aim to improve members' the learning skills and network in the field of computing.
\item Mentored chapter members.
\end{tightemize}
\sectionsep

\runsubsection{Momentum Learning}
\descript{| Teaching Assistant }
\location{Jun 2017 – Jun 2017 | Houston, TX}
\begin{tightemize}
\item Assisted Dr. Bulent Dogan for teaching Scratch Programming to elementary school students from 3-5 grade.
\end{tightemize}
\sectionsep

\runsubsection{North American University}
\descript{| Algorithms Course Instructor}
\location{Jan 2017 – May 2017 | Houston, TX}
\begin{tightemize}
\item Organized and lead Algorithms Course
\item Taught essential algorithms and data structures by using C/C++ languages.
\item Prepared lecture plan, and practice assignments.
\end{tightemize}
\sectionsep

\runsubsection{NAU ACM Bioinformatics Lab}
\descript{| Undergraduate Researcher}
\location{Sep 2015 – Feb 2017 | Houston, TX}
\begin{tightemize}
\item Participated and assisted in organizing regular meeting \& activities.
\item Focused on necessary skills for a Bioinformatician/ Computational Biologist
\end{tightemize}
\sectionsep

\runsubsection{North American University}
\descript{| Python Course Instructor}
\location{Jan 2016 – May 2016 | Houston, TX}
\begin{tightemize}
\item Taught Python Programming Language to 7 students.
\item Prepared lecture plan, and practice assignments.
\item Issued a certificate to students who complete the course.
\end{tightemize}
\sectionsep

\runsubsection{Girls Who Code}
\descript{| Chapter Instructor}
\location{Sep 2015 – May 2016 | Houston, TX}
\begin{tightemize}
\item Taught HTML/CSS, Python language to high school students from 9 to 12 grade.

\end{tightemize}
\sectionsep
\fi

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Cornell Robot Learning Lab}
\descript{| Head Undergrad Research}
\location{Jan 2014 – Present | Ithaca, NY}
Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
\sectionsep

\runsubsection{Cornell Phonetics Lab}
\descript{| Head Undergraduate Researcher}
\location{Mar 2012 – May 2013 | Ithaca, NY}
Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
\sectionsep
\fi

\iftrue
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2014	     & 23\textsuperscript{th} place  & National University Entrance Exam, Turkey\\
2010	     & 72\textsuperscript{th} place  & National High School Entrance Exam, Turkey\\
\end{tabular}
\sectionsep
\fi


\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2014   & National   & The Global Leadership and Education Forum (tGELF)\\
2012   &  National  & Golden Key International Honor Society\\
2012   &  National   & National Society of Collegiate Scholars\\
\end{tabular}
\sectionsep
\fi

\end{minipage} 
\end{document}  \documentclass[]{article}